PANCHANGE_analysis

### 2020-08-19 PANCHANGE_analysis.Rmd
added some frequency calculations and mean scores for change per disorder

@@

```{r gather to long format}
dat.long <- dat %>%
  gather(
    key = "Disorder",
    value = "Diagnosis",
    all_of(disorder_columns)) %>%
  select(
    ID,
    Sample,
    Disorder,
    Diagnosis
  )

@@

Define disorder columns in vector
```{r}
dat.long %>%
  group_by(Disorder) %>%
  count()
```

## Disorders - Frequencies *use this as example to convert chunk above*
```{r Disorders - Frequencies}
#0 = No to disorder; 1 = Yes to disorder
PMAD_na_drop_Dx %>%
  select(ID, #need to add columns for which you want summaries for - ASK GB & KY what they want in descriptives table
         dem.sex,
         starts_with("mhd.") & ends_with("numeric")) %>%
  gather(
    key = "Disorder",
    value = "Diagnosis",
    mhd.MDD_numeric:mhd.ADHD_numeric #all the columns that we want to be gathered
  ) %>%
  group_by(Disorder) %>%
  count(Diagnosis) #count for diagnoses
```

@@

Ethnicity
```{r}

Gender
```{r}

Education
```{r}

Key worker status
```{r}

COVID test positive
```{r}

COVID probable diagnosis
```{r}

@@

>>>>

```{r}
diff_score_cols <- dat %>%
  select(contains("diff_score")) %>% 
  colnames()

diff_score_cols
```

@@

```{r gather to long format}
dat.long <- dat %>%
  gather(
    key = "Disorder",
    value = "Diagnosis",
    all_of(disorder_columns)) %>%
  select(
    ID,
    Sample,
    Gender,
    Ethnicity,
    all_of(diff_score_cols),
    Disorder,
    Diagnosis
  )

@@

Define disorder columns in vector

```{r Disorder by Gender}
dat.long %>%
  filter(Diagnosis == 1) %>%
  group_by(Disorder, Gender) %>%
  count(Disorder)
```

```{r Disorder by Sample}
dat.long %>%
  filter(Diagnosis == 1) %>%
  group_by(Disorder, Sample) %>%
  count(Disorder)
```

```{r Disorder by Ethnicity}
dat.long %>%
  filter(Diagnosis == 1) %>%
  group_by(Disorder, Ethnicity) %>%
  count(Disorder)
```

## Disorders - Frequencies *use this as example to convert chunk above*
```{r Disorders - Frequencies}
#0 = No to disorder; 1 = Yes to disorder
dat.long %>%
  select(ID, #need to add columns for which you want summaries for 
         dem.sex,
         starts_with("mhd.") & ends_with("numeric")) %>%
  gather(
    key = "Disorder",
    value = "Diagnosis",
    mhd.MDD_numeric:mhd.ADHD_numeric #all the columns that we want to be gathered
  ) %>%
  group_by(Disorder) %>%
  count(Diagnosis) #count for diagnoses
```

@@

Ethnicity
```{r}
dat %>%
  group_by(Ethnicity, Sample) %>%
  count(Ethnicity)
```

Gender
```{r}
dat %>%
  group_by(Gender, Sample) %>%
  count(Gender)
```

highest_education
```{r}
dat %>%
  group_by(highest_education, Sample) %>%
  count(highest_education)
```

Key worker status
```{r}
dat %>%
  group_by(key_worker, Sample) %>%
  count(key_worker)
```

COVID test positive
```{r}
dat %>%
  group_by(respiratory.throat_swab_test_nose, Sample) %>%
  count(respiratory.throat_swab_test_nose)
```

```{r}
dat %>%
  group_by(respiratory.results_antibody_test, Sample) %>%
  count(respiratory.results_antibody_test)
```

COVID probable diagnosis
```{r}
dat %>%
  group_by(covid_probable_case_incl_screening, Sample) %>%
  count(covid_probable_case_incl_screening)
```

@@

```{r}
dat.long %>%
  filter(Diagnosis == 1) %>%
  group_by(Disorder) %>%
  summarise(
    gad_base_retro = mean(gad.diff_score_base_retro, na.rm = T),
    gad_prepan_retro = mean(gad.diff_score_prepan_retro, na.rm = T),
    gad_prepan_base = mean(gad.diff_score_prepan_base, na.rm = T),
    phq_base_retro = mean(phq.diff_score_base_retro, na.rm = T),
    phq_prepan_retro = mean(phq.diff_score_prepan_retro, na.rm = T),
    phq_prepan_base = mean(phq.diff_score_prepan_base, na.rm = T)
    )
```
